Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-26 supplement.tex
Finish response letter

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{1000 nucleotides, 17 hours (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Equal mutation rate and number of mutations, 19 hours (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Per-nucleotide mutation rate of 1.0 / crown age, 19 hours (main example)}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{1000 nucleotides, 16 hours (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Equal mutation rate and number of mutations, 16 hours (main example)}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Per-nucleotide mutation rate of 1.0 / crown age, 16 hours (main example)}
\end{figure}
